Case Study: ChIP-seq Differential Peak Calling (csaw)

### 2018-04-06 datasets/ChIP-seq/ChIPseq-CBP-csaw.Rmd
Fix typos in ChIPseq cpb Rmd code causing errors

```{r}
fqfiles <- file.path(datdir, basename(fqurls))
meta <- data.frame(genotype = factor(c("wt", "wt", "ko", "ko")),
                   fqurl = fqurls, fqfile = fqfiles,
                   bamfile = gsub("\\.fastq\\.gz", ".bam", fqfiles),
                   sortedfile = gsub("\\.fastq\\.gz", ".sorted.bam", fqfiles))
```

@@

    ## use correlateReads to determine fragment length (remove dups)
    x <- correlateReads(b_meta$sortedfile, param = reform(param, dedup = TRUE))
    frag_len <- which.max(x) - 1

    ## count reads in sliding windows (keep dups)
    win_cnts <- windowCounts(meta$sortedfile, param = param, width = 10, ext = frag.len)

@@

```{r}
if (file.exists(filtered_file)) {
    filtered_cnts <- readRDS(filtered_file)
    normfacs <- readRDS(normfacs_file)
} else {
    ## filter windows by abundance
    bins <- windowCounts(meta$sortedfile, bin = TRUE, width = 10000, param = param)
    filter_stat <- filterWindows(win_cnts, bins, type = "global")
    keep <- filter_stat$filter > log2(3)
    filtered_cnts <- win.data[keep, ]

>>>>

```{r}
fqfiles <- file.path(datdir, basename(fqurls))
meta <- data.frame(genotype = factor(c("wt", "wt", "ko", "ko")),
                   fqurl = fqurls, fqfile = fqfiles,
                   bamfile = gsub("\\.fastq\\.gz", ".bam", fqfiles),
                   sortedfile = gsub("\\.fastq\\.gz", ".sorted.bam", fqfiles),
                   stringsAsFactors = FALSE)
```

@@

    ## use correlateReads to determine fragment length (remove dups)
    x <- correlateReads(meta$sortedfile, param = reform(param, dedup = TRUE))
    frag_len <- which.max(x) - 1

    ## count reads in sliding windows (keep dups)
    win_cnts <- windowCounts(meta$sortedfile, param = param, width = 10, ext = frag_len)

@@

```{r}
if (file.exists(filtered_file)) {
    filtered_cnts <- readRDS(filtered_file)
    normfacs <- readRDS(normfacs_file)
} else {
    ## filter windows by abundance
    bins <- windowCounts(meta$sortedfile, bin = TRUE, width = 10000, param = param)
    filter_stat <- filterWindows(win_cnts, bins, type = "global")
    keep <- filter_stat$filter > log2(3)
    filtered_cnts <- win_data[keep, ]
